\documentclass[12pt]{article}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\parindent}{0in}
\setlength{\parskip}{\baselineskip}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{booktabs,multirow}

\title{CMSC 478 - HW1}

\begin{document}

CMSC 304 Fall 2019\hfill Homework \#5\\
Robert Rose

\hrulefill

\begin{enumerate}
\item Section 1: Ethics and Risk
  \begin{enumerate}
  \item[1.1] I would say it's impossible to tell whether or not the patients had
        informed consent or not due to the absence of an institutional review
        board, but it's very likely they did not. The lack of an IRB, and the 
        fact that Terri Warren had great concerns with their methodology means
        that Halford was likely unaware of the risks himself, especially
        considering he was treating patients with both strains of Herpes. The
        symptoms experienced by Erkelens, and Halford's reaction to it, also 
        support that Halford wasn't aware of the risks enough himself to
        provide informed consent to anyone else.
        
  \item[1.2] I would say the advantages did not outweigh the risks because it seems
        like much of the data collected from the Saint Kitts study will need to
        be discarded because Halford used poor methodology in his haste to 
        complete the study before he died. While the article says the FDA's job
        isn't to punish, the fact that the symptom data was self-reported rather
        than collected by followup appointments means the data reported in the
        first clinical trial will likely fail to meet the FDA's validity 
        requirements, and will likely mean people got hurt and exposed to risk
        for no reason. Additionally since the company is being sued by harmed 
        patients for not providing informed consent, the entire future of the
        vaccine is at risk. Had Halford followed best practices in the study, 
        I would say the risks presented by dodging regulators would have been
        acceptable.
  \item[1.3] The risks were not justly distributed. While the risks in any clinical
        study are typically mostly on the patients, the fact that Halford was
        dying meant that he would likely escape any consequences for the study,
        both professional, legal and personal.
  \end{enumerate}

\item Section 2: Distribution of Responsibility
  \begin{enumerate}
    \item[2.1] No.
    \item[2.2] According to effectiveness.
  \end{enumerate}

\end{enumerate}
\end{document}