\documentclass[12pt]{article}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\parindent}{0in}
\setlength{\parskip}{\baselineskip}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{booktabs,multirow}

\title{CMSC 478 - HW1}

\begin{document}

CMSC 304 Fall 2019\hfill Homework \#5\\
Robert Rose

\hrulefill

\begin{enumerate}
\item Section 1: Ethics and Risk

  \begin{enumerate}
  \item[1.1] I would say it's impossible to tell whether or not the patients had
        informed consent or not due to the absence of an institutional review
        board, but it's very likely they did not. The lack of an IRB, and the 
        fact that Terri Warren had great concerns with their methodology means
        that Halford was likely unaware of the risks himself, especially
        considering he was treating patients with both strains of Herpes. The
        symptoms experienced by Erkelens, and Halford's reaction to it, also 
        support that Halford wasn't aware of the risks enough himself to
        provide informed consent to anyone else.
        
  \item[1.2] I would say the advantages did not outweigh the risks because it seems
        like much of the data collected from the Saint Kitts study will need to
        be discarded because Halford used poor methodology in his haste to 
        complete the study before he died. While the article says the FDA's job
        isn't to punish, the fact that the symptom data was self-reported rather
        than collected by followup appointments means the data reported in the
        first clinical trial will likely fail to meet the FDA's validity 
        requirements, and will likely mean people got hurt and exposed to risk
        for no reason. Additionally since the company is being sued by harmed 
        patients for not providing informed consent, the entire future of the
        vaccine is at risk. Had Halford followed best practices in the study, 
        I would say the risks presented by dodging regulators would have been
        acceptable.
        
  \item[1.3] The risks were not justly distributed. While the risks in any clinical
        study are typically mostly on the patients, the fact that Halford was
        dying meant that he would likely escape any consequences for the study,
        both professional, legal and personal.
        
  \end{enumerate}

\item Section 2: Distribution of Responsibility

  \begin{enumerate}
    \item[2.1] No, this is not an example of the Problem of Many Hands, partially
        because there aren't really many hands here. The primary fault lies with
        the researcher, Halford, as he did most of the work in the vaccine development
        and preparation. The only "hand" involved would be the doctor who administered
        the actual vaccine in Saint Kitts, though they may not have been fully informed
        as to what they were doing. While the Hollywood investor, Fernandez, shares some
        blame for enabling him, Halford operated so far outside the norms that he
        surely should have known he was acting unethically. Especially after the meeting
        with Warren where she pointed out to him the flaws an IRB would have caught.
        
    \item[2.2] The active responsibilities distributed in this case are distributed 
        according to effectiveness rather than moral fairness. While patients seeking
        alternative treatments are expecting that some treatments may be risky, they are
        expecting that the doctors and researchers involved are not behaving in a way that
        would endanger them anymore so. I would say the doctor administering the treatments
        would have had some responsibility to ensure that best practices were being followed
        under distribution by moral fairness as well. While the researcher isn't part of this
        question, under a morally fair distribution of risk Halford would have properly
        retained an institutional review board in order to ensure that the research
        was conducted ethically and appropriately.
  \end{enumerate}

\end{enumerate}
\end{document}