\documentclass[12pt]{article}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\parindent}{0in}
\setlength{\parskip}{\baselineskip}

\usepackage{amsmath,amsfonts,amssymb}

\title{CMSC 471 - HW3}

\begin{document}

CMSC 471 Spring 2018\hfill Homework \#3\\
Robert Rose (02/13)

\hrulefill

\begin{enumerate}
\item \textbf{3.15} Consider a state space where the start state is number 1 and each state is $k$ has two successors: the numbers $2k$ and $2k + 1$
  \begin{enumerate}
  \item Draw the portion of the state space for states 1 to 15.
  \item Suppose the goal state is 11. List the order in which nodes will be visited for breadth-first search, depth-limited search with limit 3, and iterative deepening search.
  \item How well would bidirectional search work on this problem? What is the branching factor in each direction of the bidirectional search?
  \item Does the answer to (c) suggest a reformulation of the problem that would allow you to solve the problem of getting from state 1 to a given goal state with almost no search?
  \item Call the action going from $k$ to $2k$ Left, and the action from going to $2k + 1$ Right. Can you find an algorithm that outputs the solution to this problem without any search at all?
  \end{enumerate}
\newpage

\item \textbf{3.26} Consider the unbounded version of the regular 2D grid shown in Figure 3.9. The start state is at the origin, (0,0), and the goal state is at ($x$, $y$).
  \begin{enumerate}
  \item What is the branching factor $b$ in this state space?
  \item How many distinct states are there at depth $k$ (for $k > 0$)?
  \item What is the maximum number of nodes expanded by breadth-first tree search?
  \item What is the maximum number of nodes expanded by breadth-first graph search?
  \item Is $h = \left|u - x\right| + \left|v - y\right|$ an admissible heuristic for a state at ($u, v$)? Explain.
  \item How many nodes are expanded by A* graph search using $h$?
  \item Does $h$ remain admissible if some links are removed?
  \item Does $h$ remain admissible if some links are added between nonadjacent states?
  \end{enumerate}

\end{enumerate}
\end{document}