---
title: "boston_housing"
author: "Rob Rose"
date: "September 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework \#1

This is the CMSC 478 HW number one. I was asigned Problem 10 fg&h.

## Problem 10

### Part (a)

```{r part_10a}
library(MASS)
?Boston
```

### Part (b)


```{r part_10b, echo=FALSE}
attach(Boston)
pairs(~crim + zn + indus + nox + rm + age + dis + rad + tax + ptratio + black + lstat + medv)
```

Some of them look to be highly correlated, such as zn and medv. Some are highly
negatively correlated like lstat and medv, which makes sense knowing what those 
values are.

### Part (c)

```{r part_10c}
cor(Boston)
```

Most of the factors (except for the `chas` variable) are pretty correlated, 
the highest correlations are `rad` and `tax`.

### Part (d)

```{r part_10d}
summary(Boston)
```

### Part (e)

```{r part_10e}
sum(Boston$chas)
```

### Part (f)

```{r part_10f}
summary(ptratio)
```

Answer: `19.05`

### Part (g)

```{r part_10g}
Boston[Boston$medv == min(Boston$medv), ]
```

There are two that have the minimum value, and they both have very high crime per
capita. You can also see the effects of segregationist housing policies here as
the `ptratio` and `nox` are both in the third quartile.

### Part (h)

```{r part_10h}
sum(Boston[,"rm"]>7)
sum(Boston[,"rm"]>8)
```

Greater than 7: 64

Greater than 8: 13