\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineering Intern}
    {Acalvio Technologies}
    {Santa Clara, CA}
    {May 2018 - Present}
    {
      \begin{cvitems}
        \item {Developed a cloud cybersecurity deception platform for AWS, Google Cloud and Microsoft Azure.}
        \item {Used Python 3 with SQLAlchemy and Flask to store cloud computing workloads in PostgreSQL.}
        \item {Enabled deception deployment in Kubernetes clusters, including in Google Kubernetes Engine and in AWS EKS.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Naval Surface Warfare Center, Dahlgren Division}
    {Dahlgren, VA}
    {May 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Integrated customer feedback into existing Python desktop application.}
        \item {Worked with Python libraries such as: matplotlib, NumPy, pandas, tkinter and ReportLab.}
        \item {Obtained Interim Secret security clearance.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Naval Research Laboratory}
    {Washington, DC}
    {May 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Worked on search-and-rescue robots in the Navy Center for Applied Research in Artificial Intelligence.}
        \item {Developed an Android application to send commands to groups of robots over ZeroMQ pub/sub sockets.}
        \item {Used Google Play Services and Android Location Services to retrieve location data.}
      \end{cvitems}
    }
\end{cventries}
